\section{Quality attributes} 
\label{sec:quality_attributes}

This section will handle all of the \textbf{Quality attributes}, also called non-functional attributes.  In difference to section \ref{sec:functional_requirements}-\ref{sec:external_interface_requirements} that describe what the new system shall do, the quality attributes describe how the system shall be. \cite{idi.ntnu}  Quality attributes can i.e. describe uptime requirements, system architecture and security requirements.
Below, the \textbf{Quality attributes} for the WOMS system are listed. The requirements are categorized into security, safety, reliability and availability. The ID for the quality attributes are QA-\{number\}, where QA stands for quality attributes.

\begin{center}
\begin{longtable}{|c|p{4cm}|p{2cm}|c|p{1.5cm}|c|c|}
\caption{Quality attributes}
\label{table:5_requirements}\\
\hline
\textbf{ID}& \textbf{Description} & \textbf{Comment} & \textbf{Category} & \textbf{RBP*}&\textbf{Priority} & \textbf{Dependencies}\\
\hline
\endfirsthead

\multicolumn{7}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
\textbf{ID}& \textbf{Description} & \textbf{Comment} & \textbf{Category} & \textbf{RBP*}&\textbf{Priority} & \textbf{Dependencies}\\
\hline
\endhead

\hline \multicolumn{7}{r}{\textit{Continued on next page}} \\
\endfoot

\multicolumn{6}{l}{\textit{* - Related Business Process}} \\
\endlastfoot

\hline

QA-1	& The WOMS shall have at least $95\%$ rate of picking the most appropriate field technician & Validated through testing &	Reliability & \ref{sec:bp3}&Must & FR-DM-10\\
\hline
QA-2	& The WOMS shall always dispatch the highest prioritized WO first to field technicians. & Validated through testing & Reliability &\ref{sec:bp3} & Must & - \\
\hline
QA-3	& The WOMS shall have an overall uptime of at least $99\%$ each month. & Validated through testing & Availability &\ref{sec:bp1}, \ref{sec:bp2}, \ref{sec:bp3}, \ref{sec:bp4}, \ref{sec:bp5}, \ref{sec:bp6} & Must & - \\
\hline
QA-4	& The WOMS shall SQL-parse all input data so harmful inputs will not affect the database & Validated through testing , SQL-parsing means removing all illegal syntax from the text. & Safety &\ref{sec:bp1}, \ref{sec:bp2}, \ref{sec:bp3}, \ref{sec:bp4}, \ref{sec:bp5}, \ref{sec:bp6} & Must & - \\
\hline
QA-5	& The WOMS shall only allow 3 authorization attempts from each IP before the IP address is blocked for 15 minutes. & Validated through testing & Security &\ref{sec:bp1}, \ref{sec:bp2}, \ref{sec:bp3}, \ref{sec:bp4}, \ref{sec:bp5}, \ref{sec:bp6} &Must & - \\
\hline
QA-6	& The WOMS shall automatically logout a user if inactive, no input, for 15 minutes. & Validated through testing & Security &\ref{sec:bp1}, \ref{sec:bp2}, \ref{sec:bp3}, \ref{sec:bp4}, \ref{sec:bp5}, \ref{sec:bp6} & Must & - \\
\hline
QA-7	& The WOMS shall have customizable security settings for each user. & Validated through testing. Settings regarding, if allowed to edit, allowed to read or allowed to delete WOs. & Security & \ref{sec:bp1}, \ref{sec:bp2}, \ref{sec:bp3}, \ref{sec:bp4}, \ref{sec:bp5}, \ref{sec:bp6}&Must & - \\
\hline
QA-8	& Connections from outside of the ACME LAN to the WOMS shall be encrypted with TLS 1.2 & Validated through testing. & Security & \ref{sec:bp3}, \ref{sec:bp4}, \ref{sec:bp5}&Must & - \\
\hline

\end{longtable}
\end{center}



